Distributions

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
updates using the tidy data for lcoations

# Data ----------------------------------------------------
# The script for this data is in the data-raw folder
load("data/ptpl.rda")

ptpl %>%
  filter(., mpm != 0) -> ptpl
```

@@

ind_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
  #geom_line(aes(x = mpm, group = id), color = "grey", stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

fam_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = fam_g, color = fam_g), stat = "density", alpha = 0.8) +
  #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

fam_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  #geom_line(aes(x = mpm, group = fam_g, color = fam_g), stat = "density", alpha = 0.8) +
  geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

pp.boot.fits %>% 
  dplyr::select(loglik, n, kpars, dist, fgroup, boot) %>% 
  distinct() %>% 
  group_by(boot, dist) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
  transmute(dist = dist,
            BIC = BIC,
            boot = boot,
            model = "PP") %>% 
  bind_rows(., pp.boot.fits %>% 
  dplyr::select(loglik, n, kpars, dist, fgroup, boot, dBIC) %>% 
  distinct() %>% 
  filter(., dBIC == 0) %>% 
  group_by(boot) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
  transmute(dist = "multi",
            BIC = BIC,
            boot = boot, 
            model = "PP")) %>% 
  group_by(boot) %>% 
  mutate(., deltaBIC = signif(BIC - min(BIC), 3)) %>% 
  ungroup() %>% 
  arrange(boot) -> pp.bic

@@

```{r Figure3, fig.width=12, fig.height=6}

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC == 0) %>% 
  group_by(model) %>% 
  count(dist) %>% 
  mutate(prcnt_support = n/nboots) %>%
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  scale_fill_manual(values = cols.fig2) +
  geom_col() +
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Pooling Level", y = "Percent Support") +
  theme(axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>%
               filter(., model == "CP"),
             aes(x = model, y = -0.05, label = dist)) -> pooling.support

@@

pp.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
  group_by(fgroup, boot) %>%
  distinct() %>%
  group_by(fgroup) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "PP"),
             aes(x = ID, y = -0.05, label = dist)) +
  scale_fill_manual(values = cols.fig2) -> pp.support

np.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
  group_by(individual, boot) %>%
  distinct() %>%
  group_by(individual) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "NP"),
             aes(x = ID, y = -0.05, label = dist)) +
  scale_fill_manual(values = cols.fig2)  -> np.support

@@

p2_angles <- ptpl %>% 
  drop_na(rel.angle) %>% 
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  facet_wrap(~fam_g, nrow = 2) +
  theme(axis.text = element_blank()) +
  labs(title = "Partial pooling")

>>>>

# Data ----------------------------------------------------
# The script for this data is in the Orig_data_KH
load("Ch2_distributions/Orig_data_KH/tidy_data.RData")

ptpl %>%
  mutate(T_minutes = dt/60,
         Bird_ID = id,
         mpm = dist/T_minutes,
         R2n = lead(R2n)) %>%
  filter(mpm != 0) %>%
  group_by(Bird_ID) %>%
  add_tally() %>%
  filter(n >= 30) -> ptpl
```

@@

ind_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = id, color = sgroup), stat = "density", alpha = 0.8) +
  #geom_line(aes(x = mpm, group = id), color = "grey", stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

fam_dens_plot <- ptpl %>%
  drop_na(sgroup) %>% 
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = sgroup, color = sgroup), stat = "density", alpha = 0.8) +
  #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

fam_dens_plot <- ptpl %>%
  drop_na(sgroup) %>% 
  ggplot(., aes((x = mpm))) +
  #geom_line(aes(x = mpm, group = fam_g, color = fam_g), stat = "density", alpha = 0.8) +
  geom_line(aes(x = mpm, group = sgroup), color = "grey",stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

@@

pp.boot.fits %>% 
  dplyr::select(loglik, n, kpars, dist, group, boot) %>% 
  distinct() %>% 
  group_by(boot, dist) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
  transmute(dist = dist,
            BIC = BIC,
            boot = boot,
            model = "PP") %>% 
  bind_rows(., pp.boot.fits %>% 
  dplyr::select(loglik, n, kpars, dist, group, boot, dBIC) %>% 
  distinct() %>% 
  filter(., dBIC == 0) %>% 
  group_by(boot) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
  transmute(dist = "multi",
            BIC = BIC,
            boot = boot, 
            model = "PP")) %>% 
  group_by(boot) %>% 
  mutate(., deltaBIC = signif(BIC - min(BIC), 3)) %>% 
  ungroup() %>% 
  arrange(boot) -> pp.bic

@@

```{r Figure3, fig.width=12, fig.height=5}

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC == 0) %>% 
  group_by(model) %>% 
  count(dist) %>% 
  mutate(prcnt_support = n/nboots) %>%
  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
  scale_fill_manual(values = cols.fig2, drop = FALSE) +
  geom_col() +
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Pooling Level", y = "Percent Support") +
  theme(axis.title.x = element_blank()) +
  geom_label(data = bestmodel %>%
               filter(., model == "CP"),
             aes(x = model, y = -0.05, label = dist), size = 2.5) -> pooling.support

@@

pp.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, group, boot) %>%
  group_by(group, boot) %>%
  distinct() %>%
  group_by(group) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots) %>%
  ggplot(., aes(x = group, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "PP"),
             aes(x = ID, y = -0.05, label = dist), size = 2.5) +
  scale_fill_manual(values = cols.fig2) -> pp.support

np.boot.fits %>%
  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
  group_by(individual, boot) %>%
  distinct() %>%
  group_by(individual) %>%
  filter(dBIC == 0) %>%
  count(dist) %>%
  mutate(prcnt_support = n/nboots,
         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>%
  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
  geom_col() +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = scales::percent) +
  geom_label(data = bestmodel %>% filter(., model == "NP"),
             aes(x = ID, y = -0.05, label = dist), size = 2.5) +
  scale_fill_manual(values = cols.fig2)  -> np.support

@@

p2_angles <- ptpl %>% 
  drop_na(rel.angle) %>% 
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  facet_wrap(~group, nrow = 2) +
  theme(axis.text = element_blank()) +
  labs(title = "Partial pooling")
